Eclipse Che for Fair and Easy Education

### 2019-05-04 paper.tex
Raw transcription of Conclusion and Future Work

\section{Demonstrationen}
\label{sec:demos}
Das Symbol für Potenzmengen ($\powerset$) wird korrekt angezeigt.
Es ist kein Weierstraß-p ($\wp$) mehr.

>>>>

\section{Conclusion}
Cloud technology will be dominant in the foreseeable future. 
Not \textit{everything} will be best fit for cloud, but most of the everyday software benefits from the concepts. 
With more and more tools making it easier, it's just a matter of time until cloud-tec becomes standard instead of bonus.
With Eclipse Che many problems about teaching students these Cloud Skills and reducing the initial scope for learning, are addressed. 
While the impacts on motivation and the actual learning results are only hypothetical, most of the technical aspects are solved by Che.  
As Eclipse Che is cutting edge it whatsoever lacks many quality of life features, has some bugs, and the design is undefined to some extend. 
It somewhat is a chance: 
Instances like a university can have massive impact on the design of Che and drive the project to some extend for their own needs. 
With faculties working on the open source project, either providing code and features, or just testing Che in educational environments, both quality issues and missing features can be solved.    
Now cloud development is only for corporations. 
There is hardly any chance to successfully learn it at university. 
With Che there is another chance to “get back into the game” – and provide corporation-free education.  
While this sounds harsh towards companies, I think unbiase education for students is not a nice thing to have, but a core concept of education in general. 
Only if that is true, the students can make unbiased decisions and make unbiased research. 
Being dependent on Google for Universities is in a similar way disturbing, as if a biology faculty would be sponsored by Bayer. 
One can only imagine a grim future if the curriculum is influenced by profit. 
\section*{Future Work}
As this paper only summarizes benefits and outlines some ideas, the next step would be to put it to the test.
In addition, a study could be elaborated on both the acceptance and effect of a CI/CD based development course with Che. 
Unfortunately, the study would lack any comparison as there are few courses on this topic. 
These studies could be done with universities and corporations, which 
may yield very different results.   
\section{Demonstrationen}
\label{sec:demos}
Das Symbol für Potenzmengen ($\powerset$) wird korrekt angezeigt.
Es ist kein Weierstraß-p ($\wp$) mehr.
